\begin{innerlist}



\item [[Medrano et al., 2021]]\textbf{Pronóstico de Series de Tiempo de Imágenes de Sequías Utilizando Autocodificadores y Redes Neuronales} \textit{(Manuel Medrano, Juan J Flores Romero, Hector Rodríguez, Rodrigo López Farías, Carlos Lara Álvarez)}. (ISSN: 1870-4069). {Research in Computing Science}, DOI pendiente.  Currently available in Hard Copy. \url{https://www.rcs.cic.ipn.mx/} \textbf{Mexico City, July 2021}. 

\item [[Lopez-Farias et al., 2021]]\textbf{Parameter Calibration of the Patch Growing Algorithm for Urban Land Change Simulations} \textit{Rodrigo López-Farías, Sergio I. Valdez-Peña, Alberto García Robledo}. (ISSN: pendiente). {IEEE Encuentro Nacional de Computación 2021}, DOI pendiente.  Verificar en: \url{https://bit.ly/2WXOTPm}. \textbf{Morelia, México, Agosto 2021}. 

\item [[Lamphar et al., 2021]] \textbf{A methodology for a light pollution network with optimal sensor location} \textit{Héctor Lamphar, Rodrigo López-Farías}. (ISSN: pendiente). {Artificial Light At Night 2021},  \url{https://bit.ly/3xCXSn6}.  \textbf{España, Junio 2021}. 

\item [[Vazques-Vera et al., 2020]] \textbf{Design of a Low-cost Air Quality Remote Monitoring System based on IOT and Sensor Sensitivity Validation.} \textit{Jorge L. Vázquez-Vera, Javier Díaz-Carmona, Alejando Espinoza-Calderón, Rodrigo López-Farías, Iván Y. Hernández-Paniagua}. 

DOI:10.1109 / ROPEC50909.2020.9258685, 
\url{https://ieeexplore.ieee.org/document/9258685}. {IEEE ROPEC 2020}, \textbf{Ixtapa, México} \textbf{Octubre 2020}. 



\item [[Lopez Farias et al, 2019]] \textbf{Automatic Modelling of Land Use Suitability Using Deep Feedforward Networks with Leon and
Silao, Guanajuato Region Data} \textit{Rodrigo López-Farías, Juan A. Pichardo-Corpus, Raúl A. Aguilar-Vilchis}. (ISSN: 2515-1762). {International Conference on Geospatial Information Sciences 2019}, \url{http://bit.ly/2KHxelY},\textbf{Mérida, México, Octubre 2019}. 

\item [[Lopez-Farias et al., 2019]]\textbf{Adaptive Nearest Neighbors Phase Space Reconstruction for Short-Time Prediction in Chaotic Time Series} \textit{Rodrigo López-Farías, José R. Cedeño Gonzalez, Olivia Delgadillo Ruiz, Juan J. Flores}.  .{The 10th International Multi-Conference on Complexity, Informatics and Cybernetics}, (ISBN-13: 9781941763957, \url{https://bit.ly/2ZzV0uM}), \textbf{Orlando, Estados Unidos, Marzo 2019}.


\item [[Perez-Rosas et al., 2017]] \textbf{Parameter Identification and Qualitative Analysis with Differential Evolution of the Calcium Standard Kinetics Model} \textit{Norma C. Perez-Rosas, Rodrigo López-Farías, Agustín Guerrero-Hernández and Juan J. Flores}.  .{IEEE Autumn Meeting on Power, Electronics and Computing}, (DOI: 10.1109/ROPEC.2017.8261647) (\url{https://ieeexplore.ieee.org/document/8261647}) \textbf{Ixtapa México, Noviembre 2017}.


\item [[Flores et al., 2016]] \textbf{Comparison of Time Series Forecasting Techniques with respect to Tolerance to Noise.} \textit{Juan J. Flores, Felix Calderon Solorio, Jose Rafael Cede\~no Gonzalez, Jose Ortiz Bejar and Rodrigo Lopez Farias}. (DOI: 10.1109/ROPEC.2016.7830618) {IEEE Autumn Meeting on Power, Electronics and Computing}, (\url{https://ieeexplore.ieee.org/document/7830618}), \textbf{Ixtapa México, Noviembre 2016}.




\item[[Rodriguez-Rangel et al., 2016]] \textbf{Combined holt-winters and GA trained ANN approach for sensor validation and reconstruction: Application to water demand flowmeters} \textit{Hector Rodriguez-Rangel, Vicen\c{c} Puig, Juan J. Flores and ,  Rodrigo López} Farías. 10.1109/SYSTOL.2016.7739751. {3rd International Conference on Control and Fault-Tolerant Systems}.  (\url{https://ieeexplore.ieee.org/document/7739751}) .\textbf{Barcelona, España. Septiembre 2016}.

%\item \textbf{+8 artículos entre 2010 y 2016}

\item [[Rodriguez-Rangel et al., 2016]] \textbf{Flow meter Data Validation and Reconstruction using Neural Networks: Application to the Barcelona Water Network} \textit{Hector Rodriguez Rangel, Vicen\c{c} Puig,Juan J. Flores and ,  Rodrigo López Farías.} European Control Conference, (\url{https://ieeexplore.ieee.org/document/7810543/}) Aalborg. Denmark, Junio 2016. .

\item [[Lopez-Farias et al., 2015]] \textbf{Qualitative and Quantitative Multi-Model Forecasting with Nonlinear Noise Filter Applied to Water Demand}, \textit{Rodrigo López Farías, Juan J. Flores and Vicen\c{c} Puig}.   \textit{IEEE Autumn Meeting on Power, Electronics and Computing}. DOI: 10.1109/ROPEC.2015.7395122. (\url{https://ieeexplore.ieee.org/document/7395122}). \textbf{Ixtapa México, Noviembre 2015}.

\item [[Flores et al., 2015]]\textbf{FNN a Fuzzy Version of the Nearest Neighbour Time Series Forecasting Technique } \textit{Juan J. Flores, Jose Ortiz Bejar, Jose Rafael Cedeño, Carlos Lara-Alvarez and Rodrigo López Farías}. {IEEE Autumn Meeting on Power, Electronics and Computing}. DOI: 10.1109/ROPEC.2015.7395125. (\url{https://ieeexplore.ieee.org/document/7395125/}), \textbf{Ixtapa México, Noviembre 2015 }.

\item [[Lopez-Farias et al., 2015b]]\textbf{A Multiple-Model Predictor Approach Based on an On-Line Mode Recognition with Application to Water Demand Forecasting} \textit{Rodrigo López Farías, Vicen\c{c} Puig}.  {International work-conference on Time Series 1. 
} \url{https://goo.gl/njWQ1e}. \textbf{Granada España, Julio 2015}.

\item [[Lopez-Farias et al., 2015a]]\textbf{An implementation of a multi-model predictor based on the qualitative and quantitative decomposition of the time-series.} \textit{Rodrigo. López, Vicen\c{c} Puig, Hector Rodriguez.}  {International work-conference on Time Series 1. (\url{https://bit.ly/3xBmaxQ}). 
} \textbf{Granada España, Julio 2015}.

%\item [[Flores et al., 2011b]] \textbf{Optimization with gravitational Interactions} \textit{Dr, Juan Flores, Rodrigo López, Julio Barrera.}   {ROPEC XIII: Autumn Meeting of Electric power systems, electronic and computation ( Reunión de Oto\~no de Potencia, Electrónica y Computación)} \textbf{ Morelia México, Noviembre 2011}.

\item [[Flores et al., 2011a]] \textbf{Gravitational Interactions Optimization.} Juan Flores, Rodrigo Lopez, Julio Barrera. {Learning and Intelligent OptimizatioN}  (LION 5) DOI 10.1007/978-3-642-25566-3\_17. (\url{https://bit.ly/3E9YUJO}). \textbf{Roma, Italia - Enero 2011}. 

\item [[Flores et al., 2010]] \textbf{Particle swarm optimization with gravitational interactions for multimodal and unimodal problems.} Juan J. Flores, Rodrigo Lopez and Julio Barrera.  In {Proceedings of the 9th Mexican International Conference on Artificial Intelligence (MICAI 2010)}, pages 3361-370. Springer-Verlag. DOI 10.1007/978-3-642-16773-7\_31. (\url{https://bit.ly/31aM5kc}) \textbf{Pachuca, México. Noviembre 2010.}

\end{innerlist}
